### 2016-09-18 paper.tex
Add VS for all Neary refs; towards #72

    \bibitem{Hill2014}
    Hill C, Neary V, Gunawan B, Guala M, Sotiropoulos F.
    \newblock {U.S.} {D}epartment of {E}nergy {R}eference {M}odel {P}rogram {RM2}:
      Experimental Results.
    \newblock St. Anthony Falls Laboratory for Wind and Water Technologies Program,
      Office of Energy Efficiency and Renewable Energy, U.S. Department of Energy;
      2014.

@@

    \bibitem{Bachant2016-RM2-data}
    Bachant P, Wosnik M, Gunawan B, Neary V. {UNH} {RM2} tow tank experiment:
      Reduced dataset and processing code; 2016.
    \newblock fig\textbf{share}.
      \url{http://dx.doi.org/10.6084/m9.figshare.1373899}.

@@

    \bibitem{Bachant2015-RM2-CAD}
    Bachant P, Wosnik M, Gunawan B, Neary V. 1:6 scale {RM2} cross-flow turbine
      {CAD} package; 2015.
    \newblock fig\textbf{share}.
      \url{http://dx.doi.org/10.6084/m9.figshare.1373870}.

>>>>

    \bibitem{Hill2014}
    Hill C, Neary VS, Gunawan B, Guala M, Sotiropoulos F.
    \newblock {U.S.} {D}epartment of {E}nergy {R}eference {M}odel {P}rogram {RM2}:
      Experimental Results.
    \newblock St. Anthony Falls Laboratory for Wind and Water Technologies Program,
      Office of Energy Efficiency and Renewable Energy, U.S. Department of Energy;
      2014.

@@

    \bibitem{Bachant2016-RM2-data}
    Bachant P, Wosnik M, Gunawan B, Neary VS. {UNH} {RM2} tow tank experiment:
      Reduced dataset and processing code; 2016.
    \newblock fig\textbf{share}.
      \url{http://dx.doi.org/10.6084/m9.figshare.1373899}.

@@

    \bibitem{Bachant2015-RM2-CAD}
    Bachant P, Wosnik M, Gunawan B, Neary VS. 1:6 scale {RM2} cross-flow turbine
      {CAD} package; 2015.
    \newblock fig\textbf{share}.
      \url{http://dx.doi.org/10.6084/m9.figshare.1373870}.
